%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simple Sectioned Essay Template
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Note:
% The \lipsum[#] commands throughout this template generate dummy text
% to fill the template out. These commands should all be removed when 
% writing essay content.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{article} % Default font size is 12pt, it can be changed here
\usepackage{geometry} % Required to change the page size to A4
\geometry{a4paper,left=2cm,right=2.0cm,top=2.5cm,bottom=2.5cm} % Set the page size to be A4 as opposed to the default US Letter
\usepackage[toc,page]{appendix}
\usepackage{graphicx} % Required for including pictures
\usepackage{booktabs}
\usepackage{float} % Allows putting an [H] in \begin{figure} to specify the exact location of the figure
\usepackage{wrapfig} % Allows in-line images such as the example fish picture
\usepackage{fancyhdr}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{lastpage}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{palatino}
\usepackage[table,xcdraw]{xcolor}
\usepackage{enumerate}
\usepackage{verbatim}

\linespread{1.0} % Line spacing
\graphicspath{{Pictures/}} % Specifies the directory where pictures are stored
\pagestyle{fancy}
\title{MCM/ICM Template}

\begin{document}
	\lhead{Team \# 1901279}
\rhead{Page \thepage \ of \pageref{LastPage}}
\cfoot{}
\maketitle
\thispagestyle{fancy}
\tableofcontents % Include a table of contents
\newpage % Begins the essay on a new page instead of on the same page as the table of contents 


\section{Introduction} % Major section
\subsection{Problem Background} % Sub-section
\input{Text/ProblemBackground}

\subsection{Our Work} % Sub-section
\input{Text/OurWork}

\section{Assumptions} % Major section
\input{Text/Assumptions}

\section{Notations} % Major section
\input{Text/Notations}

\section{Model Overview} % Sub-section
\input{Text/PART1}

\section{Analysis on Socio-Economic Factors} \input{Text/PART2}

\section{Strategy for Countering the Opioid Crisis}
\input{Text/PART3}



\section{Conclusion} % Major section

\newpage
\section{Memorandum}
\input{Text/Memo.tex}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------
\newpage
\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem{1}
Rummans, Teresa A., M. Caroline Burton, and Nancy L. Dawson. "How good intentions contributed to bad outcomes: the opioid crisis." \textit{Mayo Clinic Proceedings.} Vol. 93. No. 3. Elsevier, 2018.

\bibitem{2}
Overdose deaths involving opioids by type of opioid, United States, 2000-2015. From  \textit{CDC/NCHS National Vital Statistics System, Mortality}

\bibitem{3}
Bear J. Modeling Phenomena of Flow and Transport in Porous Media[M]. Springer, 2018.

\bibitem{4}
https://en.wikipedia.org/wiki/Lasso\_(statistics)

\bibitem{5}
Friedman, Jerome, Trevor Hastie, and Robert Tibshirani. The elements of statistical learning. Vol. 1. No. 10. New York, NY, USA:: Springer series in statistics, 2001.

\bibitem{6}
Friedman, Jerome, Trevor Hastie, and Rob Tibshirani. "Regularization paths for generalized linear models via coordinate descent." Journal of statistical software 33.1 (2010): 1.

\bibitem{7}
Kim, Seung-Jean, et al. "An Interior-Point Method for Large-Scale $\ell_1 $-Regularized Least Squares." IEEE journal of selected topics in signal processing 1.4 (2007): 606-617.

\bibitem{8}
Tang, D. H., E. O. Frind, and Edward Allan Sudicky. "Contaminant transport in fractured porous media: Analytical solution for a single fracture." Water resources research 17.3 (1981): 555-564.

\bibitem{9}
Burns, Lucy. "World Drug Report 2018 By United Nations Office on Drugs and Crime New York: United Nations, 2018.

\bibitem{10}
https://americanaddictioncenters.org/rehab-guide/addiction-statistics

\bibitem{11}
https://www.mayoclinic.org/diseases-conditions/prescription-drug-abuse/in-depth/how-opioid-addiction-occurs/art-20360372

\bibitem{12}
Hsu L C. Applying the grey prediction model to the global integrated circuit industry. Technological Forecasting and Social Change, 2003, 70(6): 563-574.

\end{thebibliography}

%----------------------------------------------------------------------------------------
\newpage
\appendix
\appendixpage
\section{Mathematical Backgrounds}
\newpage
\section{EXAMPLES(TO BE DELETED!)}
\input{Text/examples}


\end{document}